%! TEX program = lualatex
\documentclass[oneside, 11pt]{memoir}

\newlength{\pagew}
\newlength{\pageh}
\setlength{\pagew}{210mm}
\setlength{\pageh}{297mm}

\setlength{\headheight}{0pt}
\setlength{\marginparsep}{0pt}
\setlength{\marginparwidth}{0pt}
\setlength{\footskip}{0pt}

\setstocksize{\pageh}{\pagew}
\settrimmedsize{\pageh}{\pagew}{*}
\settypeblocksize{270mm}{170mm}{*}
\setlrmargins{*}{*}{1}
\setulmargins{*}{*}{1}
\setmarginnotes{0cm}{0cm}{0cm}
\checkandfixthelayout

\setbeforesecskip{1em}
\setaftersecskip{0.5em}

\usepackage[math-style=ISO, bold-style=ISO]{unicode-math}
%\setmainfont{Cooper}[
%BoldFont = Cooper-Medium.ttf,
%ItalicFont = Cooper-Italic.ttf,
%BoldItalicFont = Cooper-MediumItalic.ttf
%]
\setmainfont[Language=English]{Junicode}
\setmathfont{Garamond-Math.otf}[StylisticSet={7,9}]
\setmonofont[Scale=0.8]{Iosvmata Bold}
\usepackage[letterspace=200]{microtype}

\usepackage{enumitem}
\usepackage[french]{babel}
\usepackage{datetime2}

\AtBeginDocument{\def\labelitemi{$\bullet$}}

\usepackage[
unicode,
pdfpagelabels,
bookmarks,
hyperindex,
hyperfigures,
%colorlinks
]{hyperref}

\begin{document}
\pagestyle{empty}
\pagenumbering{gobble}
\twocolumn[
\begin{@twocolumnfalse}
  \begin{center}
    \textsc{\textls{Curriculum vitae}} \\
    \textit{of}\\
    \textsc{\huge Abdullah Uyu} \\
    \vspace{1ex}
    {\small
      %Kordonboyu Mah.\ Ankara Cad.\ 147A 59
      %34860,
      \texttt{abdullahuyu@gmail.com}
      \enspace
      05531744219
      \enspace
    İstanbul}
    \vspace{5ex}
  \end{center}
\end{@twocolumnfalse}
]
\section*{\textsc{Profile}}
\noindent
A self-disciplined mathematics senior passionate about data science and
automation, capable of communicating and working in great efficiency with
others, seeking opportunities to learn and study more backend
development, preferably with \texttt{Go} along with \texttt{Redis};
databases, preferably with cloud solutions such as \texttt{AWS/Lambda}
and \texttt{AWS/DynamoDB}.
\section*{\textsc{Education}}
\noindent
Galatasaray University, Istanbul, Department of Mathematics
(\textit{French}), Faculty of
Arts and Sciences, \textit{September 2017 -- June 2025}.
%
%Osman Nuri Hekimoğlu Anatolian High School, Konya, Fundamental Sciences
%Education, from \textit{September 2013 to June 2017}.
\section*{\textsc{Technical Capabilites}}
\begin{itemize}[leftmargin=*]
  \item Engineers API backends with \texttt{Go/Gin} and
    \texttt{Python/Flask}.
  \item Writes fluent \texttt{Python} and \texttt{R} for database
    management, data analysis, web scraping and general automation.
    Specifically, has great command on Python packages \texttt{pandas},
    \texttt{matplotlib}, \texttt{seaborn}, \texttt{numpy},
    \texttt{sympy}, \texttt{Flask} and \texttt{beautifulsoup4}; on R
    package \texttt{ggplot2}.
  \item Can compose complex, custom \texttt{SQL}.
  \item Uses \texttt{sqlite3} and \texttt{psycopg2} for database
    management.
  \item Can implement agent-based models with Python \texttt{Mesa}
    package.
  \item Uses \texttt{Emacs} and \texttt{Vim} to great extent, to edit
  source code or any kind of plain text.
  \item Plans and conducts projects with \texttt{Emacs/OrgMode}.
  Produces agenda reports and annotated calendars with it.
  \item Typesets wide variety of high quality document with \LaTeX. Uses
  \texttt{PGF/TikZ} to draw figures and graphs.
  \item Uses free and open source software; \texttt{Arch Linux} for daily
    driver, \texttt{OpenBSD} for servers. Has highly \textbf{tuned}
    working environment for rapid prototyping.
  \item Writes inductive/recursive definitions and undergraduate level
    formal proofs with them in \texttt{Lean} and \texttt{Coq}.
  \item Manages projects written in \texttt{C}, \texttt{Python},
  \texttt{Scheme} and beforementioned languages/systems with
  \texttt{git}.
  \item Reads, writes and speaks English and French fluently.
  %\item In particular, reads and writes materials in Computer Sciences,
  %Mathematics, Logic and Philosophy in fair range of sophistication.
\end{itemize}
\pagebreak
\section*{\textsc{Interests}}
\begin{itemize}[leftmargin=*]
  \item Software \textbf{verification}, \textbf{functional} programming
    languages, \textbf{type} theory.
  \item Usage of \textbf{topology} in data science.
  \item \textbf{Automata} theory, specifically \textbf{cellular}
    automata.
  %\item Reading and writing poems. Printable document of my poems
  %  compiled in a book can be found at:
  %  \url{http://oneofvalts.sdf.org/media/}. For the source code, visit
  %  its git \href{https://github.com/oneofvalts/usavurdu}{repository}.
  %\item Typesetting, typography and bookbinding.
  %\item Fountain pens, inks and papers.
  %\item Modal, microtonal music. Irish and Turkish Folk Music. I play one
  %  of the fundamental, stringed instrument of Turkish Classical Music,
  %  called
  %  \href{https://en.wikipedia.org/wiki/Turkish_tambur}{\textit{tambur}}.
\end{itemize}
\section*{\textsc{Projects}}
\begin{itemize}[leftmargin=*]
  \item For a direct list of sources,
    \href{https://github.com/oneofvalts}{here} is my Github profile.
  \item As part of my graduation project, currently formalizing
    \textbf{Desargues's Theorem in Lean}. Relevant repositories are
    \href{https://github.com/oneofvalts/desargues-doc}{here} and
    \href{https://github.com/oneofvalts/desargues}{here}.
  \item I wrote proofs of some basic propositions on equivalence classes
    and modular arithmetic in \texttt{Coq}. The code is
    \href{https://github.com/oneofvalts/equivalence-classes}{here}.
  \item I have a Youtube
    \href{https://www.youtube.com/@veryarticulateloudthinker}{channel}
    where I talk about \texttt{Lean} and document the formalizing
    Desargues's Theorem.
  \item I typeset Cashmere Exchange's
    \href{https://docsend.com/view/ryp2wmfc5yxaabep}{whitepaper} with
    \LaTeX, and formalized a process into mathematics.
  \item I have a blog at \url{http://oneofvalts.sdf.org}.
  %\item I initiated \textsc{hatirlana}, where a group of authors including me
  %resumes the past month's intellectual happenings. It is a monthly
  %publication, typeset in \LaTeX. It has a git
  %\href{https://github.com/oneofvalts/hatirlana}{repository}.
  \item I wrote \texttt{letter}, an ncurses program in \texttt{C}, for
  facilitating the bookkeeping of anagrammatic poems. It has a git
  \href{https://github.com/oneofvalts/letter}{repository}.
  %\item I host the radio show \textit{ferahfeza chronicles} at \texttt{sdf}'s
  %icecast internet radio \texttt{anonradio}, where I discuss Turkish
  %Classical Music and perform with tambur.
\end{itemize}
\vfill\hfill{}\tiny\textit{Updated \today.}
\end{document}
